Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-29 docs/ms.tex
Update ms.tex

In galaxy--galaxy lensing ,since the distortion is so weak,what people usually do is stack many lensing signals together and get the "average"
shear map,and then infers the mean mass profile of galaxy or galaxy cluster.
However with HB method we can avoid this brute averaging ,instead we can get the posterior distribution of mass profile for 
each lensing system - even though it has very arge uncertainty- we can calculate the statistical property like galaxy-mass
correlation function via this posterior distribution.

>>>>

In galaxy--galaxy lensing ,since the distortion is so weak,what people usually do is stack many lensing signals together and get the "average"
shear map,and then infers the mean mass profile of galaxy or galaxy cluster.
However with HB method we can avoid this brute averaging ,instead we can get the posterior distribution of mass profile for 
each lensing system - even though it has very large uncertainty- we can calculate the statistical property like galaxy-mass
correlation function via this posterior distribution.
